Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
spelling errors

\frame{
\frametitle{Previous Work}
\begin{itemize}
	\item Hyperflow
\pause
	\begin{itemize}
		\item Flat distributed controller architecture
		\item Appliations are agnostic to underlying state distribution
		\item Provides a logically centralized global view of the network
		\item Results in performance degradation and transient inconsistencies
	\end{itemize}
\pause
	\item Onix
\pause
	\begin{itemize}
		\item Provides flexible framework to handle controller topology
		\item Provides generic distributed state management API
		\item Provides a framework but not an approach
		\item Design decisions left to control application
	\end{itemize}
\pause
	\item Kandoo
\pause
	\begin{itemize}
		\item Two-level controller architecture
		\item Events are propagated only on subscription
		\item Applications need to be aware of hierarchy
		\item View of root controller varies with control application
	\end{itemize}
\end{itemize}
}

@@

\frame{
\frametitle{Our Approach}
\begin{itemize}
\item What is being done ? 
	\begin{itemize}
		\item It's a Replicated state machine (strong or lazy replication) architecture, which had been well studied in Distributed Systems community
		\item Past work uses DHTs (Onix), Transactional DB (Onix), DFS (Hyperflow)
	\end{itemize}
	\item We are trying to study		
	\begin{itemize}
		\item Instead of just using a general repilication mechanism, can we exploit the fact that network views are being replicated ?
		\item Could SDN datapath (replication client) make use of replication timestamps ?
	\end{itemize}

@@

\frame{
\frametitle{Timestamp}
	\begin{itemize}
		\item An example - Link Balancer Controller [4]
		\item On a flow arriving at an ingress port, a path with minimum maximum utilization is choosen
		\item Each domain $i$ maintains a vector timestamp, $T_{i}[1...n]$. $T_{i}[j]$ contains the latest revision number of domain $j$ link utilizations, seen by domain $i$
		\item Each router in a domain is updated with domain's timestamp
		\item When a flow path is being set up at domain $j$, it is augmented by the $T_{j}$
		\item When a router in a domain $i$ receives a flow with timestamp $T_{j}$, it may change part of flow's path if $T_{j}[i] < T_{i}[i]$ 
		\item Flow's timestamp is updated as $max\{T_{j}[k], T_{i}[k]\}$ , $k=1...n$ 
		\item OK, can we do better ? Yes!, a domain can change the entire flow's path according to timestamps.
	\end{itemize}   
}

>>>>

\frame{
\frametitle{Previous Work}
\begin{itemize}
	\item Hyperflow
\pause
	\begin{itemize}
		\item Flat distributed controller architecture
		\item Applications are agnostic to underlying state distribution
		\item Provides a logically centralized global view of the network
		\item Results in performance degradation and transient inconsistencies
	\end{itemize}
\pause
	\item Onix
\pause
	\begin{itemize}
		\item Provides flexible framework to handle controller topology
		\item Provides generic distributed state management API
		\item Provides a framework but not an approach
		\item Design decisions left to control application
	\end{itemize}
\pause
	\item Kandoo
\pause
	\begin{itemize}
		\item Two-level controller architecture
		\item Events are propagated only on subscription
		\item Applications need to be aware of hierarchy
		\item View of root controller varies with control application
	\end{itemize}
\end{itemize}
}

@@

\frame{
\frametitle{Our Approach}
\begin{itemize}
\item What is being done ? 
	\begin{itemize}
		\item It's a Replicated state machine (strong or lazy replication) architecture, which had been well studied in Distributed Systems community
		\item Past work uses DHTs (Onix), Transactional DB (Onix), DFS (Hyperflow)
	\end{itemize}
	\item We are trying to study		
	\begin{itemize}
		\item Instead of just using a general replication mechanism, can we exploit the fact that network views are being replicated ?
		\item Could SDN datapath (replication client) make use of replication timestamps ?
	\end{itemize}

@@

\frame{
\frametitle{Timestamp}
	\begin{itemize}
		\item An example - Link Balancer Controller [4]
		\item On a flow arriving at an ingress port, a path with minimum maximum utilization is chosen
		\item Each domain $i$ maintains a vector timestamp, $T_{i}[1...n]$. $T_{i}[j]$ contains the latest revision number of domain $j$ link utilizations, seen by domain $i$
		\item Each router in a domain is updated with domain's timestamp
		\item When a flow path is being set up at domain $j$, it is augmented by the $T_{j}$
		\item When a router in a domain $i$ receives a flow with timestamp $T_{j}$, it may change part of flow's path if $T_{j}[i] < T_{i}[i]$ 
		\item Flow's timestamp is updated as $max\{T_{j}[k], T_{i}[k]\}$ , $k=1...n$ 
		\item OK, can we do better ? Yes!, a domain can change the entire flow's path according to timestamps.
	\end{itemize}   
}
